---
title: "Homework #1 -- Pet Names Dataset"
author: "batool alsadah"
date: "14/2/2021"
output: github_document
---

**Student ID:2201003400

**Deadline:** 23:59 on Saturday, 13 February 2021

**Total Points:** 30


## Loading Packages

```{r load-packages, message = FALSE}

library(tidyverse)
library(openintro)
library(ggrepel)
```


##Exercises

`1.According to the data dictionary, how many pets are included in this dataset?


(4 points)
```{r}

```
Write your narrative here
answer 1
(52519)

`2.Again, according to the data dictionary, how many variables do we have for each pet?

(4 points)

```{r}

```
Write your narrative below
answer 2
variables {7}
`3. Copy the code provided in the homework documentation and paste it here. 

(4 points)

```{r}
seattlepets %>%
count(animal_name, sort = TRUE)


```
anser3

 1 NA            483
 2 Lucy          439
 3 Charlie       387

(10 points)
anser 4
```{r species-name-top5, eval=TRUE}
seattlepets %>%
group_by(species) %>%
count(animal_name, sort = TRUE) %>%
slice_max(n, n = 5)%>%arrange(species, n)

```

`5.  What names are more common for cats than dogs? The ones above the line or the ones below the line?

Answer5 here
oliver and lily

(4 points)

`6. Is the relationship between the two variables (proportion of cats with a given name and proportion of dogs with a given name) positive or negative? What does this mean in context of the data?

Answer here
positive , every time a dog was caaed by a name the more by a cat was called by the same name

(4 points)